Imputation of Incomplete Multilevel Data with \pkg{mice}

### 2022-12-16 Manuscript/Imputation_of_Incomplete_Multilevel_Data.Rmd
Add `hiceheckman` package

- `popmis` from the \pkg{mice} package [simulated data on perceived popularity, $n = 2,000$ pupils across $N = 100$ schools with data that are MAR, @mice];
- `impact` from the \pkg{metamisc} package [empirical data on traumatic brain injuries, $n = 11,022$ patients across $N = 15$ studies with data that are MAR, @metamisc];
- `hiv` from the \pkg{GJRM} package [simulated data on HIV diagnoses, $n = 6,416$ patients across $N = 9$ regions with data that are MNAR, @GJRM].

@@

@@

# Case study III: HIV data

Data are simulated and included in the `GJRM` package. We will use the following variables:

- `region` Cluster variable,
- `hiv` HIV diagnosis (0=no, 1=yes),
- `age` Age of the patient,
- `marital` Marital status,
- `condom` Condom use during last intercourse,
- `smoke` Smoker (levels; inclusion restriction variable).

The imputation of these date is based on the toy example from [IPDMA Heckman Github repo](https://github.com/johamunoz/Heckman-IPDMA/blob/main/Toy_example.R).

```{r hiv, echo=FALSE}
# data
data("hiv", package = "GJRM")
hiv <- hiv %>% 
  select(c("region","hiv", "age", "marital", "condom", "smoke", "interviewerID")) %>% 
  mutate(region = as.integer(region))
# md pattern
plot_pattern(hiv)
```

R=region+language+(1|InterviewID) model with interviewer as random effects, because the observations are not independent. Interviews are not allocated randomly. In theory we expect the inclusion-restriction variable to be randomly assigned, that's why we're adding region and language to compensate for non-random allocation. [TODO: Explain exclusion-restriction, refer to paper Johanna].

Load the data:
```{r}
data("obesity",  package = "miceheckman")
```

We obtain here the random effects for each interviewer, this is an approximation of the interviewer's skill which will be used as an exclusion constraint. Here, since the location of the interviewer was not randomly assigned to the subjects, the assignment was corrected for region and language.

Set the Heckman model as imputation method
```{r}
#Set prediction matrix and methods
ini <- mice(obesity, maxit = 0)
meth<-ini$method
meth["weight"]<-"2l.heckman"
pred <- ini$pred
pred["weight","cluster"]<- -2
pred["weight","rt"] <- -3
```

```{r eval=FALSE}
imp <- mice(obesity, # dataset with missing values
                        m = 10,   # number of imputations
                        maxit = 1,
                        seed = 1234, #seed attached to the dataID
                        meth = meth, #imputation method vector
                        pred = pred, #imputation predictors matrix
                        print = T,
                        meta_method="reml",
                        pmm=FALSE)
```

>>>>

- `popmis` from the \pkg{mice} package [simulated data on perceived popularity, $n = 2,000$ pupils across $N = 100$ schools with data that are MAR, @mice];
- `impact` from the \pkg{metamisc} package [empirical data on traumatic brain injuries, $n = 11,022$ patients across $N = 15$ studies with data that are MAR, @metamisc];
- `obesity` from the \pkg{miceheckman} package [simulated data on obesity, $n = 2,111$ patients across $N = 5$ regions with data that are MNAR].

@@

Install non-CRAN packages:
```{r packages}
devtools::install_github("amices/ggmice")
devtools::install_github("hanneoberman/miceheckman")
```

@@

# Case study III: obesity data

Data are simulated and included in the `miceheckman` package. We will use the following variables:

- `region` Cluster variable,
- `gender` Gender (0=male, 1=female),
- `age` Age of the patient,
- `height` Height in meters,
- `weight` Weight in kilograms,
- `rt`` Response time in minutes (inclusion-restriction variable).

The imputation of these data is based on the toy example from [IPDMA Heckman Github repo](https://github.com/johamunoz/Heckman-IPDMA/blob/main/Toy_example.R) [TODO: add reference Arxiv paper Johanna].

Load the data:
```{r obesity}
data("obesity", package = "miceheckman")
```

Select relevant variables:
```{r bmi}
dat <- select(obesity, -"bmi")
```

Visualize missing data pattern:
```{r obesity-md}
plot_pattern(dat)
```

Create predictor matrix:
```{r obesity-pred}
pred <- quickpred(dat)   # predictor matrix
pred["weight","cluster"]<- -2 # clustering variable
pred["weight","rt"] <- -3 #inclusion-restriction variable
plot_pred(pred)
```

Set the Heckman model as imputation method:
```{r meth}
meth <- make.method(dat) # methods vector
meth["weight"]<-"2l.heckman"
```

Impute the missingness:
```{r eval=FALSE}
imp <- mice(
  dat, # dataset with missing values
  m = 5, # number of imputations
  maxit = 10,
  meth = meth, #imputation method vector
  pred = pred, #imputation predictors matrix
  meta_method = "reml",
  printFlag = FALSE
)
```
